### 2025-01-16 ECE159 Lecture Notes/main.tex
Add Potential Energy-Separation Curve and update lecture notes

\documentclass[11pt]{article}
\input{preamble}
\begin{document}
\thispagestyle{empty}
{\LARGE \bf ECE 159 Lecture Notes}\\
{\large Hei Shing Cheung}\\
Fundamentals of Electric Circuits, Winter 2024 \hfill ECE 159\\
\vspace{10pt}
\section{Basic Concepts}
\subsection{Basic Defintions}
\begin{definition}[Voltage]
    The difference of the electric potential between two points in a circuit.
    \begin{equation}
        V \defeq \int_C \textbf{E} \cdot d\textbf{l}
    \end{equation}
    \end{definition}

    \begin{definition}[Current]
    Rate of change of charge at a particular point in the circuit.
    \begin{equation}
        I \defeq \frac{dq}{dt}
    \end{equation}
    \end{definition}

    \begin{definition}[Power]
    The rate of change of energy for an element in the circuit. Power is the product of voltage and current.
    \end{definition}

@@

\subsection{Resistance}
\paragraph{Ohm's Law} Ohm's Law states that the current through a resistor is proportional to the voltage across it.
\begin{equation}
    V = IR
\end{equation}
\paragraph{Resistivity} The resistance of a material is proportional to the length of the material and inversely proportional to the cross-sectional area of the material.
\begin{equation}
    R = \rho \frac{l}{A}
\end{equation}
\paragraph{Short and Open Circuits} A short circuit is a circuit with no resistance, while an open circuit is a circuit with infinite resistance.
\paragraph{Conductance} The reciprocal of resistance is conductance. The unit of conductance is mho (ohm spelled backwards), \rotatebox[origin=c]{180}{$\Omega$}.
\begin{equation}
    G = \frac{1}{R}
\end{equation}
\paragraph{Power in Resistors} The power dissipated in a resistor is given by:
\begin{equation}
    P = I^2R = \frac{V^2}{R}
\end{equation}
\paragraph{Resistors in Series} If resistors are placed in series with each other, their current must be the same, The equivalent resistance of resistors in series is the sum of the resistances.
\begin{equation}
    R_{\text{eq}} = R_1 + R_2 + \dots + R_n
\end{equation}
\paragraph{Resistors in Parallel} If resistors are placed in parallel with each other, their voltage must be the same. The equivalent resistance of resistors in parallel is the reciprocal of the sum of the reciprocals of the resistances.
\begin{equation}
    \frac{1}{R_{\text{eq}}} = \frac{1}{R_1} + \frac{1}{R_2} + \dots + \frac{1}{R_n}
\end{equation}
\paragraph{Comination of Series and Parallel Resistors} To find the equivalent resistance of a combination of series and parallel resistors, first find the equivalent resistance of the resistors in series, then find the equivalent resistance of the resistors in parallel.
\subsection{Node, Branch, and Loop}
\paragraph{} Three important ideas in electric circuit analysis are:
\begin{enumerate}
    \item \textbf{Branch}: A branch is an element in an electric circuit, such as a source or a resistor.
    \item \textbf{Node}: A point of connection of two or more branches within an electric circuit.
    \item \textbf{Loop}: Any closed path in an electric circuit. To form a loop, one must start and end at the same point and never pass through the same node twice.
\end{enumerate}
\section{DC Circuits}
\paragraph{}

>>>>

\documentclass[11pt]{article}
\input{preamble}
\begin{document}
\thispagestyle{empty}
{\LARGE \bf ECE 159 Lecture Notes}\\
{\large Hei Shing Cheung}\\
Fundamentals of Electric Circuits, Winter 2024 \hfill ECE 159\\
\vspace{10pt}
\section{Basic Concepts}
\subsection{Basic Defintions}
\begin{definition}[Voltage]
    The difference of the electric potential between two points in a circuit. The enegy required to move a charge from one point to another.
    \begin{equation}
        V \defeq \int_C \textbf{E} \cdot d\textbf{l} = \frac{dW}{dq}
    \end{equation}
    \end{definition}
    \paragraph{Polarity} The polarity is fliped as illustrated when the voltage is indicated as negative.
    \begin{definition}[Current]
    Rate of change of charge at a particular point in the circuit.
    \begin{equation}
        I \defeq \frac{dq}{dt}
    \end{equation}
    \end{definition}

    \begin{definition}[Power]
    The rate of change of energy for an element in the circuit. Power is the product of voltage and current.
    \begin{equation}
        P \defeq \frac{dW}{dt} = \frac{dW}{dq} \cdot \frac{dq}{dt} = V \cdot I
    \end{equation}
    \end{definition}

@@

\subsection{Resistance}
\paragraph{Ohm's Law} Ohm's Law states that the current through a resistor is proportional to the voltage across it.
\begin{equation}
    V = IR
\end{equation}
\paragraph{Resistivity} The resistance of a material is proportional to the length of the material and inversely proportional to the cross-sectional area of the material.
\begin{equation}
    R = \rho \frac{l}{A}
\end{equation}
\paragraph{Short and Open Circuits} A short circuit is a circuit with no resistance, while an open circuit is a circuit with infinite resistance.
\paragraph{Conductance} The reciprocal of resistance is conductance. The unit of conductance is mho (ohm spelled backwards), \rotatebox[origin=c]{180}{$\Omega$}.
\begin{equation}
    G = \frac{1}{R}
\end{equation}
\paragraph{Power in Resistors} The power dissipated in a resistor is given by:
\begin{equation}
    P = I^2R = \frac{V^2}{R}
\end{equation}
\paragraph{Resistors in Series} If resistors are placed in series with each other, their current must be the same, The equivalent resistance of resistors in series is the sum of the resistances.
\begin{equation}
    R_{\text{eq}} = R_1 + R_2 + \dots + R_n
\end{equation}
\paragraph{Resistors in Parallel} If resistors are placed in parallel with each other, their voltage must be the same. The equivalent resistance of resistors in parallel is the reciprocal of the sum of the reciprocals of the resistances.
\begin{equation}
    \frac{1}{R_{\text{eq}}} = \frac{1}{R_1} + \frac{1}{R_2} + \dots + \frac{1}{R_n}
\end{equation}
\paragraph{Comination of Series and Parallel Resistors} To find the equivalent resistance of a combination of series and parallel resistors, first find the equivalent resistance of the resistors in series, then find the equivalent resistance of the resistors in parallel.
\paragraph{Voltage Division} The voltage across a resistor in series is proportional to the resistance of the resistor.
\begin{equation}
    V_i = V \frac{R_i}{R_{\text{eq}}}
\end{equation}
\paragraph{Current Division} The current through a resistor in parallel is proportional to the conductance of the resistor.
\begin{equation}
    I_i = I \frac{G_i}{G_{\text{eq}}}
\end{equation}
\subsection{Node, Branch, and Loop}
\paragraph{} Three important ideas in electric circuit analysis are:
\begin{enumerate}
    \item \textbf{Branch}: A branch is an element in an electric circuit, such as a source or a resistor.
    \item \textbf{Node}: A point of connection of two or more branches within an electric circuit.
    \item \textbf{Loop}: Any closed path in an electric circuit. To form a loop, one must start and end at the same point and never pass through the same node twice.
\end{enumerate}
\subsection{Kirchhoff's Laws}
\paragraph{} Kirchhoff's Laws are two laws that are used to analyze electric circuits.
\paragraph{Kirchhoff's Current Law (KCL)} The sum of currents entering a node is equal to the sum of currents leaving a node.
\begin{equation}
    \sum I_{\text{in}} = \sum I_{\text{out}}
\end{equation}
\paragraph{Kirchhoff's Voltage Law (KVL)} The sum of voltages around a closed loop is equal to zero.
\begin{equation}
    \sum V_{\text{loop}} = 0
\end{equation}

\section{DC Circuits}
\paragraph{}

### 2025-01-16 ESC195 Lecture Notes/main.tex
Add Potential Energy-Separation Curve and update lecture notes

    I_n &= \int \sin^n(x) \, dx \\
    &= \int \sin^{n-1}(x) \sin(x) \, dx \\
    &= \frac{-\cos(x) \sin^{n-1}(x)}{n} + \frac{(n-1)}{n} \int \cos^2(x) \sin^{n-2}(x) \, dx \\

@@

@@

@@

@@

\section{Hyperbolic Trigonometric Functions}
\begin{definition}[Hyperbolic Sine]
    The hyperbolic sine function is defined as:
    \begin{equation} \sinh(x) = \frac{e^x - e^{-x}}{2}. \end{equation}
\end{definition}
\begin{definition}[Hyperbolic Cosine]
    The hyperbolic cosine function is defined as:
    \begin{equation}  \cosh(x) = \frac{e^x + e^{-x}}{2}. \end{equation}
\end{definition}
\paragraph{Properties} These combinations of exponential functions have properties similar to the trigonometric functions.
\paragraph{Derivatives} The derivatives of the hyperbolic functions are:
\begin{align}
    \frac{d}{dx} \sinh(x) &= \cosh(x), \\
    \frac{d}{dx} \cosh(x) &= \sinh(x).
\end{align}
\paragraph{Identities} The hyperbolic functions satisfy the following identities:
\begin{align}
    \cosh^2(x) - \sinh^2(x) &= 1, \\
    \cosh(2x) &= \cosh^2(x) + \sinh^2(x), \\
    \sinh(2x) &= 2\sinh(x)\cosh(x).
\end{align}
\paragraph{Hyperbola} The hyperbolic functions are related to the hyperbola $x^2 - y^2 = 1$. Simiar to the circle, the hyperbola can be parametrized by the hyperbolic functions (e.g. $x = \cosh(t)$, $y = \sinh(t)$).
\paragraph{Area} The area of a sector of the hyperbola is given by:
\begin{equation}
    A = t/2,
\end{equation} 
where $t$ is the angle of the sector along the parametrization $\{(x,y)\mid x = \cosh(t), y = \sinh(t)\}$.
\begin{figure}[h!]
    \begin{center}
        \begin{tikzpicture}[scale=0.8]
            % Draw the axes
            \draw[->] (-5, 0) -- (5, 0) node[right] {$x$};
            \draw[->] (0, -5) -- (0, 5) node[above] {$y$};

@@

            % Fill the sector area between hyperbola, line, and x-axis
            \fill[blue, opacity=0.3, domain=0:1, variable=\t]
                (0, 0) -- plot ({cosh(\t)}, {sinh(\t)}) -- cycle;
        \end{tikzpicture}
    \end{center}
    \caption{Sector of the hyperbola}
    \centering
\end{figure}
\paragraph{Catenary} The hyperbolic cosine function describes the shape of a hanging chain or cable. The catenary is the curve formed by a chain hanging from two points. It is given by the equation:
\begin{equation}
    a \cosh\left(\frac{x}{a}\right),
\end{equation}
\begin{definition}[Hyperbolic Tangent]
    The hyperbolic tangent function is defined as:
    \begin{equation}
        \tanh(x) = \frac{\sinh(x)}{\cosh(x)} = \frac{e^x - e^{-x}}{e^x + e^{-x}}. 
    \end{equation}
\end{definition}
\paragraph{Derivative} The derivative of the hyperbolic tangent function resembles the derivative of the regular tangent function:
\begin{equation} \frac{d}{dx} \tanh(x) = \text{sech}^2(x). \end{equation}
\paragraph{Identities} The hyperbolic tangent function satisfies the following identities:
\begin{align}
    \tanh(x) &= \frac{\sinh(x)}{\cosh(x)}, \\
    \text{sech}^2(x) &= 1 - \tanh^2(x).
\end{align}
\paragraph{Secant, Cosecant, Cotangent} The hyperbolic secant, cosecant, and cotangent functions are defined similarly to the regular secant, cosecant, and cotangent functions. They are the \textbf{reciprocal} of the hyperbolic cosine, sine, and tangent functions, respectively.
\paragraph{Inverse Hyperbolic Functions} The inverse hyperbolic functions are defined as the inverse of the hyperbolic functions. They are denoted by $\sinh^{-1}(x)$, $\cosh^{-1}(x)$, $\tanh^{-1}(x)$, etc.
\begin{align}
    \text{arsinh } x &= \ln\left(x + \sqrt{x^2 + 1}\right) \\[10pt]
    \text{arcosh } x &= \ln\left(x + \sqrt{x^2 - 1}\right) \\[10pt]
    \text{artanh } x &= \frac{1}{2} \ln\left(\frac{1 + x}{1 - x}\right) \\[10pt]
    \text{arcsch } x &= \ln\left(\frac{1}{x} + \sqrt{\frac{1}{x^2} + 1}\right) \\[10pt]
    \text{arsech } x &= \ln\left(\frac{1}{x} + \sqrt{\frac{1}{x^2} - 1}\right) \\[10pt]
    \text{arcoth } x &= \frac{1}{2} \ln\left(\frac{x + 1}{x - 1}\right)
\end{align}

\end{document}

>>>>

    I_n &= \int \sin^n(x) \, dx \nonumber \\
    &= \int \sin^{n-1}(x) \sin(x) \, dx \nonumber \\
    &= \frac{-\cos(x) \sin^{n-1}(x)}{n} + \frac{(n-1)}{n} \int \cos^2(x) \sin^{n-2}(x) \, dx \nonumber \\

@@

\paragraph{Reduction for $\cos^n(x)$} We can obtain the reduction formula of $\cos^n(x)$ via IBP.
    I_n &= \int \cos^n(x) \, dx \nonumber \\
    &= \int \cos^{n-1}(x) \cos(x) \, dx \nonumber \\
    &= \frac{\sin(x) \cos^{n-1}(x)}{n} + \frac{(n-1)}{n} \int \sin^2(x) \cos^{n-2}(x) \, dx \nonumber \\
    &= \frac{\sin(x) \cos^{n-1}(x)}{n} + \frac{(n-1)}{n} I_{n-2}

@@

\paragraph{Reduction for $\tan^n(x)$} We can obtain the reduction formula of $\tan^n(x)$ via the trigonometric identities.
    I_n &= \int \tan^n(x) \, dx \nonumber \\
    &= \int \tan^{n-1}(x) \tan(x) \, dx \nonumber \\
    &= \frac{\tan^{n-1}(x)}{n-1} - \int \tan^{n-2}(x) \, dx \nonumber \\
    &= \frac{\tan^{n-1}(x)}{n-1} - I_{n-2}
\paragraph{Reduction for $\cot^n(x)$} We can obtain the reduction formula of $\cot^n(x)$ via the trigonometric identities.
    I_n &= \int \cot^n(x) \, dx \nonumber \\
    &= \int \cot^{n-1}(x) \cot(x) \, dx \nonumber \\
    &= \frac{\cot^{n-1}(x)}{n-1} - \int \cot^{n-2}(x) \, dx \nonumber \\
    &= \frac{\cot^{n-1}(x)}{n-1} - I_{n-2}

@@

\paragraph{Weierstrass Substitution} We can solve integrals by using the Weierstrass substitution:
    \tan\left(\frac{x}{2}\right) = t \Leftrightarrow \cos(x) = \frac{1-t^2}{1+t^2} \quad \sin(x) = \frac{2t}{1+t^2} \quad dx = \frac{2dt}{1+t^2}
This substitution is useful for solving integrals with trigonometric functions, by converting them into rational functions.

@@

\subsection{Partial Fractions}
\paragraph{Partial Fraction Decomposition} We can decompose a rational function into partial fractions to simplify integration.
\paragraph{} We want to solve the integral:
    \int \frac{P(x)}{Q(x)} \, dx
, where $P(x)$ and $Q(x)$ are polynomials.
$$ \int \frac{2x^2 + 3x + 1}{x^3 + 2x^2 + x} \, dx $$
We can decompose the rational function into partial fractions:
$$ \frac{2x^2 + 3x + 1}{x^3 + 2x^2 + x} = \frac{A}{x} + \frac{B}{x+1} + \frac{C}{(x+1)^2} $$
\paragraph{} We can solve for the constants $A$, $B$, and $C$ by equating the coefficients of the partial fractions to the original function. We have:
    2x^2 + 3x + 1 &= A(x+1)^2 + Bx(x+1) + Cx \\
    \intertext{Thus, we can solve it by setting $x = 0$, $x = -1$}
\paragraph{Summary} We can solve integrals using partial fraction decomposition by following these steps:
    \textbf{Step} & \textbf{Description} \\ \hline
    1 & Factorize the denominator of the rational function. \\
    2 & Write the partial fraction decomposition. \\
    3 & Solve for the constants by equating the coefficients. \\
    4 & Integrate the partial fractions. \\ \hline
    \caption{Steps for Partial Fraction Decomposition}
\subsection{Improper Integrals}
\paragraph{Improper Integral} An improper integral is an integral with an infinite limit or a discontinuity in the interval of integration.
\paragraph{} We want to solve the integral:
    \int_a^b f(x) \, dx
, where $a$ or $b$ is infinite or $f(x)$ is discontinuous.
$$ \int_0^\infty e^{-x} \, dx $$

Evaluating the integral:
\begin{align*}
    \int_0^\infty e^{-x} \, dx &= \lim_{b \to \infty} \int_0^b e^{-x} \, dx \\
    &= \lim_{b \to \infty} -e^{-x} \Big|_0^b \\
    &= \lim_{b \to \infty} -e^{-b} + 1 \\
    &= 1
\end{align*}
\end{example}
\section{Hyperbolic Trigonometric Functions}
\begin{definition}[Hyperbolic Sine]
    The hyperbolic sine function is defined as:
    \begin{equation} \sinh(x) = \frac{e^x - e^{-x}}{2}. \end{equation}
\end{definition}
\begin{definition}[Hyperbolic Cosine]
    The hyperbolic cosine function is defined as:
    \begin{equation}  \cosh(x) = \frac{e^x + e^{-x}}{2}. \end{equation}
\end{definition}
\paragraph{Properties} These combinations of exponential functions have properties similar to the trigonometric functions.
\paragraph{Derivatives} The derivatives of the hyperbolic functions are:
\begin{align}
    \frac{d}{dx} \sinh(x) &= \cosh(x), \\
    \frac{d}{dx} \cosh(x) &= \sinh(x).
\end{align}
\paragraph{Identities} The hyperbolic functions satisfy the following identities:
\begin{align}
    \cosh^2(x) - \sinh^2(x) &= 1, \\
    \cosh(2x) &= \cosh^2(x) + \sinh^2(x), \\
    \sinh(2x) &= 2\sinh(x)\cosh(x).
\end{align}
\paragraph{Hyperbola} The hyperbolic functions are related to the hyperbola $x^2 - y^2 = 1$. Simiar to the circle, the hyperbola can be parametrized by the hyperbolic functions (e.g. $x = \cosh(t)$, $y = \sinh(t)$).
\paragraph{Area} The area of a sector of the hyperbola is given by:
\begin{equation}
    A = t/2,
\end{equation} 
where $t$ is the angle of the sector along the parametrization $\{(x,y)\mid x = \cosh(t), y = \sinh(t)\}$.
\begin{figure}[h!]
    \begin{center}
        \begin{tikzpicture}[scale=0.8]
            % Draw the axes
            \draw[->] (-5, 0) -- (5, 0) node[right] {$x$};
            \draw[->] (0, -5) -- (0, 5) node[above] {$y$};

@@

            % Fill the sector area between hyperbola, line, and x-axis
            \fill[blue, opacity=0.3, domain=0:1, variable=\t]
                (0, 0) -- plot ({cosh(\t)}, {sinh(\t)}) -- cycle;
        \end{tikzpicture}
    \end{center}
    \caption{Sector of the hyperbola}
    \centering
\end{figure}
\paragraph{Catenary} The hyperbolic cosine function describes the shape of a hanging chain or cable. The catenary is the curve formed by a chain hanging from two points. It is given by the equation:
\begin{equation}
    a \cosh\left(\frac{x}{a}\right),
\end{equation}
\begin{definition}[Hyperbolic Tangent]
    The hyperbolic tangent function is defined as:
    \begin{equation}
        \tanh(x) = \frac{\sinh(x)}{\cosh(x)} = \frac{e^x - e^{-x}}{e^x + e^{-x}}. 
    \end{equation}
\end{definition}
\paragraph{Derivative} The derivative of the hyperbolic tangent function resembles the derivative of the regular tangent function:
\begin{equation} \frac{d}{dx} \tanh(x) = \text{sech}^2(x). \end{equation}
\paragraph{Identities} The hyperbolic tangent function satisfies the following identities:
\begin{align}
    \tanh(x) &= \frac{\sinh(x)}{\cosh(x)}, \\
    \text{sech}^2(x) &= 1 - \tanh^2(x).
\end{align}
\paragraph{Secant, Cosecant, Cotangent} The hyperbolic secant, cosecant, and cotangent functions are defined similarly to the regular secant, cosecant, and cotangent functions. They are the \textbf{reciprocal} of the hyperbolic cosine, sine, and tangent functions, respectively.
\paragraph{Inverse Hyperbolic Functions} The inverse hyperbolic functions are defined as the inverse of the hyperbolic functions. They are denoted by $\sinh^{-1}(x)$, $\cosh^{-1}(x)$, $\tanh^{-1}(x)$, etc.
\begin{align}
    \text{arsinh } x &= \ln\left(x + \sqrt{x^2 + 1}\right) \\[10pt]
    \text{arcosh } x &= \ln\left(x + \sqrt{x^2 - 1}\right) \\[10pt]
    \text{artanh } x &= \frac{1}{2} \ln\left(\frac{1 + x}{1 - x}\right) \\[10pt]
    \text{arcsch } x &= \ln\left(\frac{1}{x} + \sqrt{\frac{1}{x^2} + 1}\right) \\[10pt]
    \text{arsech } x &= \ln\left(\frac{1}{x} + \sqrt{\frac{1}{x^2} - 1}\right) \\[10pt]
    \text{arcoth } x &= \frac{1}{2} \ln\left(\frac{x + 1}{x - 1}\right)
\end{align}
\appendix
\input{appendix.tex}
\end{document}

### 2025-01-16 MAT185 Lecture Notes/main.tex
Add Potential Energy-Separation Curve and update lecture notes

>>>>

\subsection{Vector Subspace}
\begin{definition}[Vector Subspace]
    Let $V$ be a vector space and $W \subseteq V$, then $W$ is a vector subspace of $V$ if $W$ is a vector space.
\begin{theorem}[Subspace Test, I]
    Let $V$ be a vector space over $\mathbb{R}$ and $W \subseteq V$ with the usual addition and scalar multiplication, then $W$ is a subspace of $V$ iff for all $\textbf{x}, \textbf{y} \in W$ and $\alpha \in \mathbb{R}$:
        \item $\textbf{x} + \textbf{y} \in W$
        \item $\alpha \textbf{x} \in W$
        \item $\textbf{0} \in W$
    ($\Rightarrow$) Assume $W$ is a subspace of $V$, then $W$ is a vector space. Thus, the axioms of vector space are satisfied. \\
    ($\Leftarrow$) Assume the three conditions are satisfied, then $W$ is a vector space. Thus, $W$ is a subspace of $V$.
\subsection{Linear combinations}
\begin{definition}[Linear Combination]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$ and $\alpha_1, \alpha_2, \ldots, \alpha_n \in \mathbb{R}$, then:
        \alpha_1 \textbf{v}_1 + \alpha_2 \textbf{v}_2 + \ldots + \alpha_n \textbf{v}_n
    is a linear combination of $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$
\begin{definition}[Linear independence]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$ and $\alpha_1, \alpha_2, \ldots, \alpha_n \in \mathbb{R}$. If the equation:
        \alpha_1 \textbf{v}_1 + \alpha_2 \textbf{v}_2 + \ldots + \alpha_n \textbf{v}_n = \textbf{0}
    has only the trivial solution $\alpha_1 = \alpha_2 = \ldots = \alpha_n = 0$.

    Then, $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$ are said to be linearly independent; otherwise, they are linearly dependent.
\end{definition}
\begin{definition}[Span]
    Let $V$ be a vector space and $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n \in V$, then:
    \begin{align*}
        \text{Span}(\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n) = \left\{ \alpha_1 \textbf{v}_1 + \alpha_2 \textbf{v}_2 + \ldots + \alpha_n \textbf{v}_n \, | \, \alpha_1, \alpha_2, \ldots, \alpha_n \in \mathbb{R} \right\}
    \end{align*}
    is the set of all linear combinations of $\textbf{v}_1, \textbf{v}_2, \ldots, \textbf{v}_n$
\end{definition}
